---
title: "R Notebook"
output: html_notebook
---

team members
Andres Jimenez ajimenezbonilla1234@floridapoly.edu
Allan Gil      agil1330@floridapoly.edu


Introduction

 

Most of us watch Netflix and enjoy watching movies and TV shows on the platform daily. Since Netflix is one of the oldest streaming platforms that are still currently available, how does one select something to watch. Netflix has a huge library of shows and movies to watch which can make this process difficult.

 

-       What is the average rating based on year?

-       What Netflix series are only for adults? 

-       What series have the highest ratings?


 

Let’s get this answered!

Our final project is for Intro to Data Science summer B class 2021.

```{r}
library(ggplot2)
library(tidyverse)
```

```{r}
netflixlink<-"netflixShows.csv"
netflixShows<- read_csv(netflixlink,    col_types = cols(ratingDescription = col_integer(), 
        release_year = col_integer(), user_rating_score = col_integer(), 
        user_rating_size = col_integer()))
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

```{r}
glimpse(netflixShows)

```

```{r}
colnames(netflixShows)
```

```{r}
summary(netflixShows)
```
different ratings 
the table below depicts the different age ratings and what they mean
```{r}
 rating_meaning<- netflixShows %>% 
  select(rating, ratingLevel )
distinct(rating_meaning)
 
```
this chart depicts all of the different shows streaming and what there age rating is 
```{r}
netflixShows %>% 
select(title,rating ) %>% 
group_by(rating ) %>% 
arrange(rating)

```
this chart shows the different rating description
```{r}
netflixShows %>% 
  distinct(ratingDescription)
```



this next plot chart shows the corraltion beteen user ratings and the avergae release date 
```{r}
 ggplot(netflixShows ,aes(x= release_year,y=user_rating_score,  )) +
  geom_point( color="#E50914",fill="#E50914")+
  labs(title = "user ratings per year ",
       x = "release  year",
       y = "user rating ",)
```

```{r}
netflixShows %>% 
  select(release_year,user_rating_score) %>% 
  group_by(release_year) %>% 
  summarise(averageRating = mean(user_rating_score,na.rm = TRUE))
```
this chart shoes the age rating of movies released each year
```{r}
ggplot(data=ratings_1,aes(y= ratingDescription,x= release_year, color= rating)) +
geom_point(color="black",binwidth=5)+
  labs(title = " diffrently rated movies per year ",
       x = "release  year",
       y = "age rating ",
       size = "age rating")

```
how many movies Netflix has per release year
```{r}
select(netflixShows, title, release_year) %>% 
  group_by(release_year) %>% 
  count(release_year)
```

```{r}
ggplot(titlenum, aes(y=n,x=release_year))+
  geom_point()+ 
  labs(title = "movies on netflix per released per year ",
       x = "release  year",
       y = "number of movies ",
       size = "")
```


what are the newest Netflix series are most suitable for children under 13?

```{r}
netflixShows %>% 
  select(title, rating, ratingLevel, ratingDescription,release_year) %>% 
  filter(ratingDescription <=70) %>% 
  arrange(desc(release_year))%>% 
  summarize(title, rating, ratingLevel)
```
there are total of 569 netflix series suitable for childern under 13.



what year has the the most movies with the highest average rating
```{r}
netflixShows %>% 
 select(release_year, user_rating_score,title) %>% 
  group_by(release_year) %>% 
  mutate(average_rating_per_year =mean(user_rating_score ,na.rm=TRUE))
```
2017 has the highest average ratings
```{r}
netflixShows %>% 
  select(release_year, user_rating_score,title) %>% 
  group_by(release_year) %>% 
  summarise(average_rating_per_year =mean(user_rating_score ,na.rm=TRUE)) %>% 
  ggplot()+
  geom_text(aes(x=average_rating_per_year,y=release_year,label=release_year))+
  labs(y= "year of ratings",x= "average rating per year",title = "Average ratings per year" )
```


How many netflix series  have a user rating score below a 60?
```{r}
netflixShows %>% 
  select(release_year, user_rating_score, title) %>% 
  filter(user_rating_score < 60)
```
A total of 27 Netflix series  have a user rating lower than 60.


How many Netflix series have not been rated?
```{r}
netflixShows %>% 
  select(release_year, rating, title) %>% 
  filter(rating == "NR")
```
A total of 14 Netflix series  have not been rated.


How Many Netflix series have a rating description greater than a 100?

```{r}
netflixShows %>% 
  select(title, rating, ratingDescription) %>% 
  filter(ratingDescription > 100)
```
A total of 163 Netflix series have a rating description greater than a 100.


conclusion
After our data exploration, we were able to gain some insight into how release year, and content rating, affect the review scores. This project has helped me and my team adapt to an online environment and github has helped with this process. In this project we further learned important R skills.    


future works 
there is more work to be done such as matching the average watch time to how the users rated the show for example this could show you how the user rated a show or movie and whether they finished it or not and use that correlation to see whether people who finished the show rated it higher than the people who did not finish. another thing you could do is find out how long certain shows or moves are and see how many people are watching those shows versus shows or moves of the same genre with different lengths. these questions and others help Netflix maximize profits on licensing contracts as well as help recommend shows for people to watch as well as help people decide what to watch.  


data sets cited 
thank you  professor Rei Sanchez-Arias for providing the netflix data set

Netflix data set: 
https://github.com/reisanar/datasets/blob/4598573c75313d32076ea86e086f2d617d9fac8f/netflixShows.csv